\documentclass[10pt,a4paper]{article}
\usepackage[english]{babel}
\usepackage{a4wide}
\usepackage{indentfirst}%缩进
\usepackage{enumerate}%加序号
\usepackage{enumitem}
\usepackage{multirow}%合并行
\usepackage{geometry}%设置页边距
\usepackage{hyperref}
\geometry{top=0.75in,bottom=0.75in,left=0.75in,right=0.75in}
\begin{document}
\begin{center}
    \Large{\textbf{Chongdan Pan}}\\
    \normalsize{panchongdan@gmail.com $\bullet$ 734-934-4277 $\bullet$ Jersey City, NJ}\\
\end{center}
\noindent
\rlap{\rule[-1mm]{\linewidth}{.5mm}}\textbf{\large{EDUCATION}}\\
\noindent\textbf{University of Michigan}\hfill Ann Arbor, MI\\
\emph{Master of Science in Information} (GPA: 4.0/4.0)\hfill\emph{Aug 2021 - Apr 2023}\\
Relevant Courses: Machine Learning, Natural Language Processing, Timeseries Analysis, Finance Engineering \\\\
\noindent
\rlap{\rule[-1mm]{\linewidth}{.5mm}}\textbf{\large{SKILLS}}\\
\textbf{Programming: }C/C++, Python, Shell, SQL, Scala, Solidity, JavaScript\\
\textbf{Frameworks/Libraries: }Numpy, Spark, PyTorch, Kafka, Django, Redis, Git\\\\
\noindent
\rlap{\rule[-1mm]{\linewidth}{.5mm}}\textbf{\large{WORK EXPERIENCE}}\\
\textbf{D. E. Shaw \& Co.}\hfill New York, NY\\
Software Developer\hfill\emph{Aug 2023 - Present}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Built frameworks and tools to enhance discretionary trading strategies.
    \item Automated job setups to analyze portfolio risk and monitor market status.
    \item Developed software and financial models to price sophisticated financial derivatives.
\end{itemize}
\noindent\\
\textbf{Jump Trading}\hfill Chicago, IL\\
Software Engineer Intern\hfill\emph{June 2022 - Aug 2022}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Researched asynchronous programming and multiprocessing to reduce network file system latency.
    \item Developed a high-performance Python library to fetch global market high-frequency trading data.
    \item Created multidimensional data manipulation and calculation tools to enhance quantitative research.
\end{itemize}
\noindent\\
\rlap{\rule[-1mm]{\linewidth}{.5mm}}\textbf{\large{RESEARCH \& PROJECTS}}\\
\textbf{Blockchain-based Peer Review System}\hfill\emph{Feb 2022 - Apr 2023}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Developed an Ethereum-based decentralized application to enhance trust between patients and doctors by recording immutable historical behaviors and reviews.
    \item Authored a book chapter \emph{Blockchain Technology for Preventing Disasters in Surgery: A Case Study on Plastic Surgery} in \href{https://link.springer.com/book/9789819720484}{\emph{Technology Innovation for Sustainable Development of Healthcare and Disaster Management}} to be published by \emph{Springer}.
    \item Led an interdisciplinary team to build an MVP software and won the finalist of Umich Ross Crypto Fintech Challenge.
\end{itemize}
\noindent\\
\textbf{Quantitative Research on Market Making}\hfill \emph{May 2021 - Apr 2023}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Built market data publishers, fair value calculators, and gateways to catch arbitrage opportunities.
    \item Applied Word2Vec and LSTM on text data to generate predictors from social media text data.
    \item Improved order book spread analysis framework for the US equity market through Xetra Liquidity Measure.

\end{itemize}
\noindent\\
\textbf{Political Misinformation Detection}\hfill \emph{Feb 2022 - Sep 2022}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Built an automated system to collect and fact-check suspicious political misinformation.
    \item Applied network and graph algorithms to identify major misinformation spread on social media.
    \item Used NLP and time series methods to predict the mass spreading of misinformation.
\end{itemize}
\noindent\\
\textbf{Entrepreneurship Research on Telepresence Robot}\hfill \emph{Apr 2021 - Aug 2021}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Built a remote care robot prototype with functions such as free movement, medicine dispensation, and vital monitoring, winning the champion of \emph{UM-SJTU JI Covid-19 Entrepreneur Challenge}.
    \item Published \href{https://ieeexplore.ieee.org/document/9330532}{\emph{Technology Entrepreneurship in Developing Countries: Role of Telepresence Robots in Healthcare}} in \emph{IEEE Engineering Management Review}.
    \item Conducted a systematic review on the application of telepresence robots, publishing \href{https://journals.lww.com/dm/fulltext/2022/08010/Telepresence_robots_to_support_telehealth_during.30.aspx}{\emph{Telepresence Robots to Support Telehealth during Pandemic}} in \emph{Digital Medicine}.
    \item Analyzed telepresence robots' role in the pandemic, authoring a book chapter \emph{Telepresence Robots for Healthy Ageing} in the IET Book \href{https://shop.theiet.org/digital-tools-and-methods-to-support-healthy-ageing}{\emph{Digital Methods and Tools for Healthy Ageing}}.
\end{itemize}
\noindent\\
\textbf{VEX Robotic Competition}\hfill\emph{Apr 2018 - Aug 2021}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Applied 3D printing, CAD design, control theory, computer vision, and C++ to build competitive robots.
    \item Led the SJTU robotic competition team to participate in the VEX Robotic championships globally.
    \item Won the Skill-challenge World Champion and Division Champion in the 2019 VEX World Championship.
    \item Achieved Tournament Champion, Excellence Award, and ASUS Future Star in the 2019 VEX Asia-open Tournament and 2018 VEX Asia-Pacific Championship. Interviewed by \href{https://www.chinadaily.com.cn/a/201902/25/WS5c73ea69a3106c65c34eb502.html}{\emph{China Daily}}, the only national English-language newspaper in China.
\end{itemize}
\end{document}
