\documentclass[10pt,a4paper]{article}
\usepackage[english]{babel}
\usepackage{a4wide}
\usepackage{indentfirst}%缩进
\usepackage{enumerate}%加序号
\usepackage{enumitem}
\usepackage{multirow}%合并行
\usepackage{geometry}%设置页边距
\usepackage{hyperref}
\geometry{top=0.75in,bottom=0.75in,left=0.75in,right=0.75in}
\begin{document}
\begin{center}
    \Large{\textbf{Chongdan Pan}}\\
    \normalsize{panchongdan@gmail.com $\bullet$ 734-934-4277 $\bullet$ Jersey City, NJ}\\
    \normalsize{\href{https://www.linkedin.com/in/pandapcd/}{www.linkedin.com/in/pcdpanda/}}
\end{center}
\noindent
\rlap{\rule[-1mm]{\linewidth}{.5mm}}\textbf{\large{EDUCATION}}\\
\noindent\textbf{University of Michigan}\hfill Ann Arbor, MI\\
\emph{Master of Science in Information} (GPA: 4/4)\hfill\emph{Apr 2023}\\
Relevant Courses: Natural Language Processing, Timeseries Analysis, Full-stack Software Design, Finance Engineering \\\\
\textbf{University of Michigan - Shanghai Jiao Tong University Joint Institute}\hfill Shanghai, China\\
\emph{Bachelor of Science in Electrical and Computer Engineering; Minor in Entrepreneurship}\hfill\emph{Aug 2020}\\
Relevant Courses: Algorithms, Operating Systems, Computer Network, Convex Optimization, Machine Learning\\\\
\noindent
\rlap{\rule[-1mm]{\linewidth}{.5mm}}\textbf{\large{SKILLS}}\\
\textbf{Programming: }C/C++, Python, Shell, SQL, Scala, Git, Solidity, Rust, JavaScript, TypeScript\\
\textbf{Third-party tools: }Redis, MongoDB, Hadoop, Alluxio, Spark, Kafka, RabbitMQ, Tableau, Clickhouse\\
\textbf{Framework/Library: }Numpy, Spark, Alluxio, Pytorch, Kafka, RabbitMQ, Django, Hardhat, Anchor\\\\
\noindent
\rlap{\rule[-1mm]{\linewidth}{.5mm}}\textbf{\large{PROFESSIONAL EXPERIENCE}}\\
\textbf{D. E. Shaw \& Co.}\hfill New York, New York\\
Software Developer\hfill\emph{Aug 2023 - present}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Build software and tools to provide fast access to tools and data for discretionary tradings.
    \item Run analysis and generate reports for market data and trading portfolio.  
    \item Develop financial models to price sophisticated financial derivatives.
\end{itemize}
\noindent\\
\textbf{Solana Lab}\hfill Ann Arbor, Michigan\\
Web3 Developer Intern\hfill\emph{June 2022 - Aug 2022}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Led a team to design and build an NFT marketplace with Solana Metaplex API in Rust and TypeScript
    \item Did NFT economy model research to realize NFT unique features with Solana smart contracts.
\end{itemize}
\noindent\\
\textbf{Jump Trading}\hfill Chicago, Illinois\\
Software Engineer Intern\hfill\emph{June 2022 - Aug 2022}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Implemented asynchronous data scanner of the network file system and reduced the latency by three times.
    \item Built user-friendly and high performance Python library to fetch global markets' bar data. 
    \item Developed multidimensional data manipulation and calculation tools for quantitative researchers.
\end{itemize}
\noindent\\
\textbf{Probquant Investment}\hfill Shanghai, China\\
Software Engineer\hfill\emph{Aug 2020 - Aug 2021}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Used lock-free queue and message broker to develop a real-time data exchange and strategy monitoring system.
    \item Built the firm-wide market data warehouse for high-frequency trading data with a throughput higher than 10GB/s.
    \item Utilized shared memory to build a stand-alone in-memory key-value database with state-of-art performance.
\end{itemize}
\noindent\\
\rlap{\rule[-1mm]{\linewidth}{.5mm}}\textbf{\large{RESEARCH}}\\
\textbf{Political Misinformation Detection}\hfill \emph{Feb 2022 - Sep 2022}
\begin{itemize}[noitemsep,topsep=0pt]
\item Built a pipeline to collect political fact-check articles and fetch related suspicious tweets.
\item Applied network and graph methods to detect suspicious misinformation spreaders on Twitter.
\item Used NLP and time series peak method to provide signals for the mass spreading of misinformation.\\
\end{itemize}
\textbf{Entrepreneurship Research on Telepresence Robot}\hfill \emph{Apr 2021 - Aug 2020}
\begin{itemize}[noitemsep,topsep=0pt]
\item Analyzed the telepresence robot's role in Covid-19 based on experiments and literature and built a remote care robot prototype with functions including free movement, medicine dispensation, and vital monitoring.
\item Published \href{https://ieeexplore.ieee.org/document/9330532}{\emph{Technology Entrepreneurship in Developing Countries: Role of Telepresence Robots in Healthcare}} in \emph{IEEE Engineering Management Review}
\item Did a systematic review on the application of telepresence robots and published \href{https://journals.lww.com/dm/fulltext/2022/08010/Telepresence_robots_to_support_telehealth_during.30.aspx}{\emph{Telepresence Robots to Support Telehealth during Pandemic}} in \emph{Digital Medicine}
\item Authored a book chapter in the IET Book \href{https://shop.theiet.org/digital-tools-and-methods-to-support-healthy-ageing}{\emph{Digital Methods and Tools for Healthy Ageing}}
\item Led a team of 5 members to beat competitors from all over the University and won the champion of \emph{UM-SJTU JI Covid-19 Entrepreneur Challenge}.\\
\end{itemize}
\textbf{Blockchain-based Peer Review System}\hfill\emph{Feb 2022 - Apr 2022}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Used Solidity to develop an Ethereum-based decentralized application with smart contracts to record the historical behavior of the reviewee for customers' reference.
    \item Authored a book chapter \emph{Blockchain Technology for Preventing Disasters in Surgery: A Case Study on Plastic Surgery} in \href{https://link.springer.com/book/9789819720484}{\emph{Technology Innovation for Sustainable Development of Healthcare and Disaster Management}} to be published by \emph{Springer} based on the idea of using Blockchain to prevent healthcare disasters.
    \item Led an interdisciplinary team of engineers, designers, and analysts to build an MVP for the project and won the finalist of Umich Ross Crypto Fintech Challenge.
\end{itemize}
\noindent\\
\rlap{\rule[-1mm]{\linewidth}{.5mm}}\textbf{\large{PROJECT EXPERIENCE}}\\
\textbf{Crypto Market Making}\hfill \emph{May 2021 - present}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Built market data publisher, fair value calculator, and gateways for multiple crypto exchanges to catch arbitrage opportunities.
    \item Used Xetra Liquidity Measure and spread analysis to improve the execution of market maker strategy.
    \item Developed hedge strategy to manage the risk of market making.
\end{itemize}
\noindent\\
\textbf{Crypto Quantitive Research}\hfill \emph{May 2021 - Apr 2023}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Used Word2Vec and LSTM on tweets data to generate meaningful predictors for crypto trading strategies.
    \item Built a data pipeline to fetch, clean, normalize and store median-frequency blockchain market and text data from Binance and Twitter Rest API.
    \item Developed a backtest system to test the performance of predictors for Barra models parallelly.
    \item Applied Garch-AR, Bretó Stochastic model to analyze the volatility of crypto market time series data.
\end{itemize}
\noindent\\
\textbf{Relic NFT}\hfill\emph{May 2022 - Apr 2023}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Working with UMich to provide NFT tickets for the match associated with the university sports team.
    \item Developed an NFT marketplace using Hardhat, Solidity, and JavaScript, supporting trades and standard ERC-721 token functions.
    \item Set up and maintained a forked Ethereum blockchain in our virtual environment to test and run the Dapp.
\end{itemize}
\noindent\\
\textbf{VEX Robotic Competition}\hfill\emph{Apr 2018 - Aug 2021}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Applied 3D printing, CAD design, control theory, computer vision, and C++ to build competitive robots.
    \item Led SJTU robotic competition team to participate in the VEX Robotic championships globally. 
    \item Won the Skill-challenge World Champion and Division Champion in 2019 VEX World Championship.
    \item Won the Tournament Champion, Excellence Award and ASUS Future Star in 2019 VEX Asia-open Tournament and 2018 VEX Asia-Pacific Championship. Interviewed by \href{https://www.chinadaily.com.cn/a/201902/25/WS5c73ea69a3106c65c34eb502.html}{\emph{China Daily}}.
\end{itemize}
\end{document}